### 2020-09-04 README.Rmd
Simplified the characterization of the properties of initial conditions. No Errors, Warnings, and 2 empty notes.

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
# Obviously you should modify the resdir to suit your own computer
resdir <- "./../../A_code/aMSEUse/out/testrun"
dirExists(resdir,make=TRUE,verbose=TRUE)
# The following function calls will ensure that there is a control.csv,
# a zone1sm\au2pop6.csv
# and region1.csv file in the data directory
ctrlfiletemplate(resdir)
zonefiletemplate(resdir)
datafiletemplate(6,resdir,filename="zone1sau2pop6.csv")

@@

resfile <- setuphtml(resdir,runname)# prepare to save and log results

plotproductivity(resdir,runname,product,glb)
biology_plots(resdir, runname, glb, zoneC)
numbersatsize(resdir, runname, glb, zoneD)

@@

runnotes <- "This is a bare-bones example."
# If you unhash the make_html call it will generate a local website 
# inside resdir and open it so you can see the results so far.
# make_html(replist=reportlist,resdir=resdir,width=500,
#          openfile=TRUE,runnotes=runnotes,verbose=FALSE,
#          packagename="aMSE",analysis="aMSE")
```

>>>>

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
# Obviously you should modify the resdir to suit your own computer
resdir <- "./../../A_code/aMSEUse/out/run1"
dirExists(resdir,make=TRUE,verbose=TRUE)
# The following function calls will ensure that there is a control.csv,
# a zone1sm\au2pop6.csv
# and region1.csv file in the data directory
ctrlfiletemplate(resdir)
zonefiletemplate(resdir)
datafiletemplate(6,resdir,filename="zone1sau2pop6.csv")

@@

resfile <- setuphtml(resdir)# prepare to save and log results

plotproductivity(resdir,product,glb)
biology_plots(resdir, glb, zoneC)
numbersatsize(resdir, glb, zoneD)

@@

runnotes <- "This is a bare-bones example."
# If you unhash the make_html call it will generate a local website 
# inside resdir and open it so you can see the results so far.
# make_html(replist=reportlist,resdir=resdir,width=500,
#          openfile=TRUE,runnotes=runnotes,verbose=FALSE,
#          packagename="aMSE",htmlname="testrun")
```
